Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel

### 2023-03-21 Article.tex
Corrected proofs after acceptance

%=================================================================
\documentclass[metals,article,submit,pdftex,moreauthors]{Definitions/mdpi}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ }
\daterevised{ } % Comment out if no revised date
\dateaccepted{ }
\datepublished{ }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\usepackage{gensymb}
\usepackage{accents}
\usepackage{xspace}
\usepackage{subcaption}
\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$\orcidC{}, Olivier Pantalé $^{1*}$\orcidA{}}

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{P. Tize Mha, P. Dhondapure, M. Jahazi, A. Tongne, O. Pantalé}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
$^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}

% Contact information of the corresponding author
\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{In the present work, a critical analysis of the most commonly used analytical models and recently introduced ANN-based models is performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
The high temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
The experimental flow curves were modeled using Johnson-Cook, Modified-Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and PTM models, as well as an ANN model.
The mean absolute relative error and root-mean-square error values were used to quantify the predictive accuracy of the models analyzed.
The results indicated that the Johnson-Cook and Modified-Zerilli-Armstrong models had a significant error, while the Hansel-Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
The ANN model showed excellent agreement between the predicted and experimental flow curves, with an error of less than 0.62\%.
To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
The Hansel-Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
However, the ANN model was the most powerful of all the models.}

% Keywords
\keyword{Artificial Neural Network; Constitutive flow Law; Analytical flow law; Interpolation; Extrapolation; Gleeble}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads \cite{tian2022deformation, tavakoli2019ferrite}.
It has also been reported that phase transformation can occur during deformation.
The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.

Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
A large number of phenomenological, semi-empirical, or physical models \cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021} have been developed.
Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive, jia2021modified, sim2022modified}.
However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{ovesy2020explicit, niu2020constitutive, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{derazkola2021review, wang2022deformation, miao2022deformation}.
The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.

The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{wu2022experimental, stoffel2020deep, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.

Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the models' efficiency.
Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different processing windows.

The present work aims to address the preceding question using the recently introduced ANN model.
To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
Then, the interpolation and extrapolation capabilities of each model are evaluated.
The results are validated based on experimental work carried out herein and on data obtained from the literature.

@@

%----------------------------------------------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------------------------------------------

The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of medium carbon steel, Fe = balance}
\begin{tabular}{lccccccc}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place. We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-1}
\caption{The inside of the Gleeble-3800 thermomechanical simulator with the specimen in place}
\label{fig:Inside-Gleeble3800}
\end{figure}

As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator}
\label{fig:GleebleProcess}
\end{figure}

The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(1+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
As raw data contains noises, the savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
To allow further use of the data in numerical simulations, elastic parts are removed.

%----------------------------------------------------------------------------------
\subsection{Compression tests results\label{sec:ComTestResults}}
%----------------------------------------------------------------------------------

>>>>

%=================================================================
\documentclass[metals,article,accept,pdftex,moreauthors]{Definitions/mdpi}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands - do not modify
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: \hl{Ji Hoon Kim} %MDPI: Please add it.
}
\datereceived{ 10 February 2023}
\daterevised{ 16 March 2023} % Comment out if no revised date
\dateaccepted{20 March 2023}
\datepublished{ }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\usepackage{gensymb}
\usepackage{accents}
\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{\alph{subfigure}}
\DeclareCaptionLabelFormat{subcaptionlabel}{\normalfont(\textbf{#2}\normalfont)}
\captionsetup[subfigure]{labelformat=subcaptionlabel}

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}
\newcommand{\hlok}[1]{\colorbox{green}{#1}}

@@

% Authors, for the paper (add full first names)
\Author{\hlok{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
$^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Tize Mha, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; \hlok{ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system. Please confirm. OK
\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., \hlok{Montréal,} %MDPI: We suggest to use English format city name. we add the department information, please confirm. OK
 QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}

% Contact information of the corresponding author
\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{In the present work, a critical analysis of the most-commonly used analytical models and recently introduced ANN-based models was performed to evaluate their predictive accuracy within and outside the experimental interval used to generate them.
The high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800.
The experimental flow curves were modeled using the Johnson--Cook, Modified-Zerilli--Armstrong, Hansel--Spittel, Arrhenius, and PTM models, as well as an ANN model.
The mean absolute relative error and root-mean-squared error values were used to quantify the predictive accuracy of the models analyzed.
The results indicated that the Johnson--Cook and Modified-Zerilli--Armstrong models had a significant error, while the Hansel--Spittel, PTM, and Arrhenius models were able to predict the behavior of this alloy.
The ANN model showed excellent agreement between the predicted and experimental flow curves, with an error of less than 0.62\%.
To validate the performance, the ability to interpolate and extrapolate the experimental data was also tested.
The Hansel--Spittel, PTM, and Arrhenius models showed good interpolation and extrapolation capabilities.
However, the ANN model was the most-powerful of all the models.}

% Keywords
\keyword{\hlok{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords. please check all the keywords. we suggest to use lowercase if the uppercase is not necessary: OK
neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
The manufacturing process of the large blocks starts with ingot casting, followed by open die forging and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size, and mechanical properties from the surface to the core of the forged block have been required.
Of the three manufacturing steps (casting, forging, and heat treatment), forging is where the most-important microstructural changes take place, which greatly influence the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads~\cite{tian2022deformation, tavakoli2019ferrite}.
It has also been reported that phase transformation can occur during deformation.
The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely the strain $\varepsilon$, the strain rate $\mdot\varepsilon$, and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.

Considering the large size of blocks, a purely experimental approach, based on trial and error, cannot be used by industry, and therefore, reliable predictive tools, such a finite element analysis (FEA) codes, have been developed and are commercially available.
However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite phase at temperatures above the dissolution temperature of most carbides.
Hence, most constitutive models depend on macroscopic parameters, which influence the hardening and softening of the material.
A large number of phenomenological, semi-empirical, or physical \mbox{models~\cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021}} have been developed.
Among these, the Johnson--Cook (JC) \cite{Johnson-1983}, Hansel--Spittel (HS) \cite{chadha2018approach}, and Zerilli--Armstrong (ZA) \cite{Zerilli-1987} models are the best-known and most-widely available in FEA codes.
Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate, and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive, Jia-2021, sim2022modified}.
However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high-temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{ovesy2020explicit, niu2020constitutive, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{derazkola2021review, wang2022deformation, miao2022deformation}.
The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high-temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.

The artificial neural network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures and depends on many factors, which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to dealing with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{wu2022experimental, stoffel2020deep, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
Although ANN models can predict well the material flow behavior, there is a problem with their implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to the strain, strain rate, and temperature.

Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problems still persist with the models' efficiency.
Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different processing windows.

The present work aimed to address the preceding question using the recently introduced ANN model.
To this end, initially, hot compression tests, simulating the open die forging process, were carried out, and the flow curves generated were modeled using the above-mentioned constitutive equations and an ANN model developed in this work.
Then, the interpolation and extrapolation capabilities of each model were evaluated.
The results were validated based on experimental work carried out herein and on data obtained from the~literature.

@@

%----------------------------------------------------------------------------------
\subsection{Experimental Procedure}
%----------------------------------------------------------------------------------

The material used in this study consisted of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[H]
\centering
\caption{Chemical composition of medium carbon steel. Fe = balance.}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
\textbf{\hlok{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
\begin{figure}[H]

\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study.}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as the lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
Figure \ref{fig:Inside-Gleeble3800} shows the inside of the Gleeble thermomechanical simulator with the specimen in place. We used 3 thermocouples soldered to the specimen to record the temperature history during the test and to ensure that the specimen was at the correct temperature prior to testing.
\begin{figure}[H]

\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-1}
\caption{The inside of the Gleeble-3800 thermomechanical simulator with the specimen in place.}
\label{fig:Inside-Gleeble3800}
\end{figure}

As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260~\celsius$ with a heating rate of $2$~\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$~\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$, and $r_t$ are the height, large radius, and small radius of the specimen after compression, respectively.
\begin{figure}[H]

\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{\textls[-25]{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator.}}
\label{fig:GleebleProcess}
\end{figure}

The stress--strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to obtain the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(1+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$ and where $F$ is the force as measured by the Gleeble load cell.
As the raw data contain noises, the savgol\_filter method from the scipy library was used to remove noise and provide smoother data.
To allow further use of the data in numerical simulations, the elastic parts were removed.

%----------------------------------------------------------------------------------
\subsection{Compression Tests' Results\label{sec:ComTestResults}}
%----------------------------------------------------------------------------------

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5~temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[H]

\includegraphics[width=0.99\columnwidth]{Figures/rawData}
\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
\label{fig:RawData}
\end{figure}
All data curves contain $700$ equidistant strain values up to $\varepsilon=0.7$.
Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of 21,000 data points.
For the identification of the parameters of all the analytical models presented in this article, we restricted the database to 35 strain values between $0.02$ and $0.7$, with a step of $0.02$ (this is illustrated in Figure \ref{fig:RawData}, where the data used correspond to the dots on the graphs).
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{galos2022review}.
The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and friction, thus, increases.
The increase of stress observed at the beginning of the deformation and up to $0.1$ is due to work hardening (WH).
After $0.1$ and up to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work hardening rate.
This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1~\ps$, except for those at $1050~\celsius$ and $1100~\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050~\celsius$ and $1100~\celsius$ and a $0.1~\ps$ strain rate; (iii) a continuous increase with significant work hardening (all deformation temperatures and strain rate of $1~\ps$).
Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels.
In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$--$5~\ps$.

Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$ minutes and rapidly cooled to room temperature. From this image, large grains can be observed.
On the other hand, Figure \ref{fig:Micrography}b shows the microstructure after compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.
To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ minutes and cooled down to $1150~\celsius$ to be held at this temperature for $1$ minute before compression.
After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.

%As an example, Figure \ref{fig:Micrography} shows the medium carbon microstructures held for $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[H]

\begin{subfigure}[b]{0.44\columnwidth}

\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{\centering Before hot compression}
\end{subfigure}
\hspace{10mm}
\begin{subfigure}[b]{0.44\columnwidth}

\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{\centering After hot compression}
\end{subfigure}
\vspace{6pt}
\caption{Optical micrographs of a medium carbon steel (\textbf{a}) before and (\textbf{b}) after hot compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.}
\label{fig:Micrography}
\end{figure}
The material is in the single-phase austenite state at all of the test temperatures examined.
The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with the experimental results.
